Condition-Based Maintenance for Systems based on Bayesian Component Models***

### 2016-10-05 cbm-rbd-paper.tex
second ref, some musings

Our model gives the lower and upper delay time distribution at $\tnow$,
so takes current system condition into account.

@@

example for Bayesian method in maintenance planning: \cite{2007:wang-jia}

@@

Wang \& Jia (2007) have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
model for delay time (time between defect and failure) is Weibull $h \sim \wei(\alpha,\beta)$,
and each of $\lambda, \alpha, \beta$ has a Gamma prior distribution.
The expected overall cost rate is then used to find a cost-optimal inspection interval.
For this they assume that failures are immediately repaired,
and defects found in an inspection are repaired during inspection.

@@

In the end they actually do not advocate to calculate the posterior expected cost rate (15),
but rather plug in posterior estimates for $\lambda, \alpha, \beta$,
so neglecting uncertainty in estimation.
%They also do not indicate how sensitive

(We do not assume a parametric distribution for delay time,
it rather arises as a consequence of the system layout and component failure distributions.)

@@

>>>>

Our model gives the lower and upper delay time distribution at $\tnow$,
taking current system condition into account.

@@

Example for Bayesian method in maintenance planning: \cite{2007:wang-jia}

@@

\begin{scriptsize}
Wang \& Jia (2007) have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
model for delay time (time between defect and failure) is Weibull $h \sim \wei(\alpha,\beta)$,
and each of $\lambda, \alpha, \beta$ has a Gamma prior distribution.
The expected overall cost rate is then used to find a cost-optimal inspection interval.
For this they assume that failures are immediately repaired,
and defects found in an inspection are repaired during inspection.

@@

In the end they actually do not advocate to calculate the posterior expected cost rate (15),
but rather plug in posterior estimates for $\lambda, \alpha, \beta$,
so neglecting uncertainty in estimation.
(We do not assume a parametric distribution for delay time,
it rather arises as a consequence of the system layout and component failure distributions.)

\end{scriptsize}

Example for Bayesian method in CBM with continuous monitoring: \cite{2011:elwany-et-al}
(exponential degradation model, whose parameters $\theta'$ and $\beta$ each have a prior
which is updated using the degradation signal history,
and use total expected infinite-horizon discounted cost to determine the maintenance policy)

\section{***summary of ASCE-ASME paper method}

sets of priors on component survival,
survival signature,
test data inclusion,
noninformatiove censoring,
set of system reliability curves as output,
wider set in case of prior-data conflict

\section{***extensions to ASCE-ASME paper}

repaired components: separate type in survival signature,
but same hyperparameter learning (using actual age).

\section{***from (set of) survival curves to maintenance decision}

infinite-horizon cost rate $g(\tau)$ (discounted as well?)
like in age-based policy:
this indicates in how much time from now ($\tnow$) it is economical to repair the system
\begin{align*}
g(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}
\end{align*}
and $\tau^* = \arg\min g(\tau) - \tnow$ is the cost-optimal repair time from now
($\Rsys(\cdot)$ is always in terms of time since system startup)

Sets of $\Rsys(t)$: need to determine sets of $g(\tau)$.
for each $\tau$, fix $\Rsys(\tau) \in [\lRsys(\tau), \uRsys(\tau)]$ and optimize $I(\tau) = \int_0^\tau \Rsys(t) \dd t$:
\begin{itemize}
\item nonpar.: $\ol{I}(\tau)$ by $\uRsys(t)$, $\ul{I}(\tau)$ by $\lRsys(t)$ until level of $\Rsys(\tau)$.
\item par.: optimize over $\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right], \ldots, \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]$\\
(is $g(\tau)$ indeed monotone in $\ykzfun{1}, \ldots \ykzfun{K}$?)
\end{itemize}

From sets of $g(\tau)$ to (set of) $\tau^*$:
worst case, best case, interval (how?)

Or, alternatively, simple 95\% policy? repair time from now such that system failure probability is below 5\%

\section{Case study / numerical example}

what system layout? something that demonstrates the power of the method (complex layout) or something simple?

complex: e.g., bridge system where each of the four elements is a two out of three, and the bridge element is a two-parallel.

@@

\section*{Bibliography}
